### 2023-08-18 cv/cv-body.tex
Max paper
Add doi
Move pub to published

\begin{description}
\tightlist
\item[2023]
Liu, O.R. E.J. Ward, \textbf{S.C. Anderson}, K.S. Andrews, L.A.K.
Barnett, S. Brodie, G. Carroll, J. Fiechter, M.A.\ Haltuch, C.J. Harvey,
E.L. Hazen, P.Y. Hernvann, M. Jacox, I.C. Kaplan, S. Matson, K. Norman,
M.P. Buil, R.L. Selden, A.O. Shelton, J.F. Samhouri. Species
redistribution creates unequal outcomes for multispecies fisheries under
projected climate change.
\url{https://doi.org/10.21203/rs.3.rs-2399110/v1}.
\item[2022]
\textbf{Anderson, S.C.}, E.J. Ward, P.A. English, L.A.K. Barnett.
sdmTMB: an R package for fast, flexible, and user-friendly generalized
linear mixed effects models with spatial and spatiotemporal random
fields. bioRxiv 2022.03.24.485545.
\url{https://doi.org/10.1101/2022.03.24.485545}.
\item[2022]
Lindmark, M., \textbf{S.C. Anderson}, M. Gogina, M. Casini. Evaluating
drivers of spatiotemporal individual condition of a bottom-associated
marine fish. bioRxiv 2022.04.19.488709.
\url{https://doi.org/10.1101/2022.04.19.488709}.
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

>>>>

\begin{description}
\tightlist
\item[2022]
\textbf{Anderson, S.C.}, E.J. Ward, P.A. English, L.A.K. Barnett.
sdmTMB: an R package for fast, flexible, and user-friendly generalized
linear mixed effects models with spatial and spatiotemporal random
fields. bioRxiv 2022.03.24.485545.
\url{https://doi.org/10.1101/2022.03.24.485545}.
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

Liu, O.R. E.J. Ward, \textbf{S.C. Anderson}, K.S. Andrews, L.A.K.
Barnett, S. Brodie, G. Carroll, J. Fiechter, M.A.\ Haltuch, C.J. Harvey,
E.L. Hazen, P.Y. Hernvann, M. Jacox, I.C. Kaplan, S. Matson, K. Norman,
M.P. Buil, R.L. Selden, A.O. Shelton, J.F. Samhouri. Species
redistribution creates unequal outcomes for multispecies fisheries under
projected climate change. Science Advances 9(33): eadg5468.
\url{https://doi.org/10.1126/sciadv.adg5468}.
Lindmark, M., \textbf{S.C. Anderson}, M. Gogina, M. Casini. Evaluating
drivers of spatiotemporal variability in individual condition of a
bottom-associated marine fish, Atlantic cod (\emph{Gadus morhua}). ICES
Journal of Marine Science. In press.
\url{https://doi.org/10.1093/icesjms/fsad084}.
